Registered Report

### 2024-11-12 Registered Report.Rmd
Added Spearman correlation tests.

# Add a rug plot to the bottom of the density plot to show the individual data points that make up the distribution
rug(q_scores_df$averaged_q_scores)
```

>>>>

# Add a rug plot to the bottom of the density plot to show the individual data points that make up the distribution
rug(q_scores_df$averaged_q_scores)

# Perform Spearman rank correlation test
cor_test_result <- cor.test(q_scores_df$sampled_q_maternal, 
                           q_scores_df$sampled_q_paternal, 
                           method = "spearman")

# Print the correlation test result
print(cor_test_result)
```
